---
title: "Case_Study_2"
output: 
  html_document:
    keep_md: true
    author: Brian Treadway
    date: 1/16/2020
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mosaic)
library(pander)
library(car)
library(DT)
library(ggplot2)
library(dplyr)
library(gapminder)

```
## Background

Well, this was difficult. I thought it was going to be easy after the first one but the second one was rather difficult. With very little experience with ggPlots, I was able to learn about what it takes to put everything together. I definitely got more comfortable putting the pieces together for most of it. Getting the lines and the dots together was something cool, especially adding in the sizes. I do have difficulties still adding the black dots with the right graph. 


## Images

Below is the data for Gapminder
```{r}
datatable(gapminder)
gapminder1<- filter(gapminder, country != "Kuwait")

```

```{r}
ggplot(data = gapminder1)+
  geom_point(mapping = aes(x = lifeExp, y = gdpPercap, color = continent, size = pop/100000))+
  facet_wrap(~year, nrow=1)+
  scale_y_continuous(name = "GDP Per Cap", limits = c(300, 50000),trans = "sqrt")+
  scale_x_continuous(name = "Life Expectancy", limits = c(20,80))+
  theme_bw()
ggsave("plot1.png", width = 15)
```

```{r}
gapminder2<- gapminder1 %>% 
  group_by(continent, year) %>% 
  mutate(wm= weighted.mean(gdpPercap, pop))
ggplot(data = gapminder2)+
  geom_path(mapping = aes(x= year, y = gdpPercap, color = continent))+
  geom_point(mapping = aes(x = year, y = gdpPercap, color = continent))+
  geom_path(mapping = aes(x = year, y = wm))+
  geom_point(mapping = aes(x = year, y = wm, size = pop))+
  scale_y_continuous(trans = "sqrt")+
  facet_wrap(~continent, nrow = 1)+
  theme_bw()
ggsave("plot2.png", width = 15)
```

```{r}

```

